Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Renamed the count variable to "num_of_studies"

## Breakdown of studies before and after 2005
```{r}
before_2005 <- compact_data_with_citation_keys_no_fmd %>% 
  select(publication_year) %>% 
  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
  count(before_2005) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front")

>>>>

## Breakdown of studies before and after 2005
```{r}
before_2005 <- compact_data_with_citation_keys_no_fmd %>% 
  select(publication_year) %>% 
  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
  count(before_2005, name = "num_of_studies") %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front")
